Notes

### 2021-02-11 supCLT-ind.tex
update supCLT-ind.tex

\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in}
\calclayout
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{mathrsfs}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{comment}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\begin{document}
\title
[stable CLT for super-OU processes, II]
{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes, II}
\author
[Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
{Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address{
	Yan-Xia Ren \\
	LMAM School of Mathematical Sciences \& Center for Statistical Science \\
  	Peking University \\
  	Beijing 100871, P. R. China}
\email{yxren@math.pku.edu.cn}
\thanks{Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF}
\address{
  	Renming Song \\
  	Department of Mathematics \\
  	University of Illinois at Urbana-Champaign \\
  	Urbana, IL 61801, USA}
\email{rsong@illinois.edu}
\thanks{Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
\address{
  	Zhenyao Sun \\
  	School of Mathematics and Statistics\\
  	Wuhan University\\
  	Wuhan, Hubei 430072, P. R. China. }
\address{
  	Faculty of Industrial Engineering and Management\\
  	Technion, Israel Institute of Technology \\
  	Haifa 3200003, Israel}
\email{zhenyao.sun@gmail.com}
\thanks{Zhenyao Sun is the corresponding author}
\address{
  	Jianjie Zhao \\
  	School of Mathematical Sciences \\
  	Peking University \\
  	Beijing 100871, P. R. China}
\email{zhaojianjie@pku.edu.cn}

\begin{abstract}
	This paper is a continuation of our recent paper (Elect. J. Probab. \textbf{24} (2019), no. 141) and is devoted to the asymptotic behavior of a class of supercritical super Ornstein-Uhlenbeck processes $(X_t)_{t\geq 0}$ with branching mechanisms of infinite second moment. 
	In the aforementioned paper, we proved stable central limit theorems for  $X_t(f) $ for {\it some} functions $f$ of polynomial growth in three different regimes. 
	However, we were not able to prove central limit theorems for $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
	In this note, we show that the limiting stable random variables in the three different regimes are independent, and as a consequence, we get stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
\end{abstract}
\subjclass[2010]{60J68, 60F05}
\keywords{superprocesses, Ornstein-Uhlenbeck processes, stable distribution, central limit theorem, law of large numbers, branching rate regime}
\maketitle

@@

	Denote by $\mathcal P \subset L^2(\varphi)$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
$\mathcal{P}
  	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.$
	Define
	$\mathcal C_\mathrm s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \},
		~
	\mathcal C_\mathrm c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $, and
	$ \mathcal C_\mathrm l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
	Note that $\mathcal C_\mathrm s$ is an infinite dimensional space, $ \mathcal C_\mathrm l$ and $\mathcal C_\mathrm c$ are finite dimensional spaces, and $\mathcal C_c$ might be empty.
	Define a semigroup
\begin{align}\label{e:Tt}
	T_t f
	:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
	\quad t\geq 0, f\in \mathcal P,
\end{align}
	and a family of functionals
\begin{align}\label{eq:M.13}
	m_t[f]
	:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-iT_u f(x)\big)^{1+\beta} \varphi(x) \mathrm dx,
	\quad 0 \leq t< \infty, f\in \mathcal P.
\end{align}
%{
%	The non-integer power of the complex numbers above is has its usual meaning. For the reader's convenience, we recall the its definition here.
	Let us recall the definition of the non-integer power of complex numbers here.
%}	
	For each $z\in \mathbb C\setminus (-\infty, 0]$, we define $\log z : = \log |z| + i \arg z$ where $\arg z \in (-\pi,\pi)$ is uniquely determined so that $z = |z|e^{i \arg z}$. 
	For each $z\in \mathbb C\setminus (-\infty, 0]$ and $\gamma \in \mathbb R$, we define $z^\gamma := e^{\gamma \log z}$.
	For each $\gamma \geq 0$, we define $0^\gamma := \lim_{z\to 0, z\in \mathbb C\setminus (-\infty,0]} z^\gamma=\mathbf 1_{\gamma = 0}$.

@@

%{
%\bigskip
%\noindent
% {\bf Acknowledgments:}  
\subsection*{Acknowledgment}
We thank the referees for the very helpful comments.
%}
\begin{thebibliography}{10}

@@

\bibitem{RenSongSunZhao2019Stable}
	Y.-X. Ren, R. Song, Z. Sun and J. Zhao,
	\emph{Stable central limit theorems for super Ornstein-Uhlenbeck processes},
	Elect. J Probab., \textbf{24} (2019), no. 141, 1--42.

>>>>

\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in}
\calclayout
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{mathrsfs}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{comment}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\begin{document}
\title
[stable CLT for super-OU processes, II]
{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes, II}
\author
[Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
{Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address{
	Yan-Xia Ren \\
	LMAM School of Mathematical Sciences \& Center for Statistical Science \\
  	Peking University \\
  	Beijing 100871, P. R. China}
\email{yxren@math.pku.edu.cn}
\thanks{Yan-Xia Ren is supported in part by NSFC 
(Grant Nos. 11731009 and 12071011) 
and LMEQF}
\address{
  	Renming Song \\
  	Department of Mathematics \\
  	University of Illinois at Urbana-Champaign \\
  	Urbana, IL 61801, USA}
\email{rsong@illinois.edu}
\thanks{Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
\address{
  	Zhenyao Sun \\
  	School of Mathematics and Statistics\\
  	Wuhan University\\
  	Wuhan, Hubei 430072, P. R. China. }
\address{
  	Faculty of Industrial Engineering and Management\\
  	Technion, Israel Institute of Technology \\
  	Haifa 3200003, Israel}
\email{zhenyao.sun@gmail.com}
\thanks{Zhenyao Sun is the corresponding author}
\address{
  	Jianjie Zhao \\
  	School of Mathematical Sciences \\
  	Peking University \\
  	Beijing 100871, P. R. China}
\email{zhaojianjie@pku.edu.cn}

\begin{abstract}
	This paper is a continuation of our recent paper 
(Electron. J. Probab. \textbf{24} (2019), no. 141)
and is devoted to the asymptotic behavior of a class of supercritical super Ornstein-Uhlenbeck processes $(X_t)_{t\geq 0}$ with branching mechanisms of infinite second moment.
	In the aforementioned paper, we proved stable central limit theorems for  $X_t(f) $ for {\it some} functions $f$ of polynomial growth in three different regimes.
	However, we were not able to prove central limit theorems for $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
	In this note, we show that the limiting stable random variables in the three different regimes are independent, and as a consequence, we get stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
\end{abstract}
\subjclass[2010]{60J68, 60F05}
\keywords{superprocesses, Ornstein-Uhlenbeck processes, stable distribution, central limit theorem, law of large numbers, branching rate regime}
\maketitle

@@

	Denote by $\mathcal P \subset L^2(\varphi)$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
$\mathcal{P}
  	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.$
	Define
	$\mathcal C_\mathrm s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \},
		~
	\mathcal C_\mathrm c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $, and
	$ \mathcal C_\mathrm l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
	Note that $\mathcal C_\mathrm s$ is an infinite dimensional space, $ \mathcal C_\mathrm l$ and $\mathcal C_\mathrm c$ are finite dimensional spaces, and $\mathcal C_c$ might be empty.
	Define a semigroup
\begin{align}\label{e:Tt}
	T_t f
	:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
	\quad t\geq 0, f\in \mathcal P,
\end{align}
	and a family of functionals
\begin{align}\label{eq:M.13}
	m_t[f]
	:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-iT_u f(x)\big)^{1+\beta} \varphi(x) \mathrm dx,
	\quad 0 \leq t< \infty, f\in \mathcal P.
\end{align}
	Let us recall the definition of the non-integer power of complex numbers here.
	For each $z\in \mathbb C\setminus (-\infty, 0]$, we define $\log z : = \log |z| + i \arg z$ where $\arg z \in (-\pi,\pi)$ is uniquely determined so that $z = |z|e^{i \arg z}$.
	For each $z\in \mathbb C\setminus (-\infty, 0]$ and $\gamma \in \mathbb R$, we define $z^\gamma := e^{\gamma \log z}$.
	For each $\gamma \geq 0$, we define $0^\gamma := \lim_{z\to 0, z\in \mathbb C\setminus (-\infty,0]} z^\gamma=\mathbf 1_{\gamma = 0}$.

@@

\subsection*{Acknowledgment}
We thank the referees for the very helpful comments.
\begin{thebibliography}{10}

@@

\bibitem{RenSongSunZhao2019Stable}
	Y.-X. Ren, R. Song, Z. Sun and J. Zhao,
	\emph{Stable central limit theorems for super Ornstein-Uhlenbeck processes},
 Electron. J. Probab.,
\textbf{24} (2019), no. 141, 1--42.
